Fifteen years of decentralization attempts

### 2014-03-20 table.tex
Redesigned the table

@@

		Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline
		Freenet & 2001 & no & yes, implementations are based on the FCP (Freenet Client Protocol) & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & yes\\ \hline
		Tapestry & 2001 & no & yes & yes, several applications are based on it such as OceanStore and Bayeux & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
		Pastry & 2001 & no & yes & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
		Anonymizing peer-to-peer proxy (AP3) & 2004 & no & no & no & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & yes\\ \hline
		Tarzan & 2002 & no & no(?) & no & ? & yes\\ \hline
		MorphMix & 2002 & no & yes & no & yes, although depending on the number of colluding malicious nodes & yes\\ \hline
		I2P & 2003 & no & yes & yes & ? & yes\\ \hline
		Salsa & 2006 & no & ? & ? & ? & ?\\ \hline
		Tribler & 2008 & no, based on BitTorrent & yes & yes & ? & not yet\\ \hline
		Torks & 2009 & yes & implementation exists, but not public(?) & no & ? & yes\\ \hline
		NISAN & 2009 & no & no & no & ? & yes\\ \hline
    \end{longtable}
\end{center}

>>>>

\begin{landscape}

@@

		Gnutella & ~2000 & & \checkmark & \checkmark & Vulnerable for DDoS attacks and attacks from misbehaving peers & \\ \hline
		Freenet & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \checkmark\\ \hline
		Tapestry & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \\ \hline
		Pastry & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \\ \hline
		Anonymizing peer-to-peer proxy (AP3) & 2004 & & & & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & \checkmark\\ \hline
		Tarzan & 2002 & & & & ? & \checkmark\\ \hline
		MorphMix & 2002 & & \checkmark & & yes, although depending on the number of colluding malicious nodes & \checkmark\\ \hline
		I2P & 2003 & & \checkmark & \checkmark & ? & \checkmark\\ \hline
		Salsa & 2006 & & ? & ? & ? & ?\\ \hline
		Tribler & 2008 & & \checkmark & \checkmark & ? & not yet\\ \hline
		Torks & 2009 & \checkmark & & & ? & \checkmark\\ \hline
		NISAN & 2009 & & & & ? & \checkmark\\ \hline
    \end{longtable}
\end{center}

\end{landscape}
